---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nacleanr

<!-- badges: start -->
<!-- badges: end -->

The goal of nacleanr is to **Removes Variables with Missing Values** above user defined limit from a dataset .

## Installation

You can install the released version of nacleanr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("nacleanr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("anandjage/nacleanr")
```
## Example ```perecnt_na()```

This is a basic example which shows how to find percentage of missing values in the form of NA in each variable:

```{r percent_na}
library(nacleanr)
## basic example code
sample_data <- read_data(path = system.file("extdata", 'nadata.csv', package = "nacleanr"))
percent_na(sample_data)
```



## Example ```invalidcols(dataset,threshold)```
This is a basic example which shows variables that contain missing values NA in the form more than user defined threshold

```{r invalidcols}
library(nacleanr)
nacleanr::invalidcols(data = sample_data,threshold = 50)
```

## Example ```validcols(dataset,threshold)```
This is a basic example which shows variables that contain missing values NA in the form within the user defined threshold.

```{r validcols}
nacleanr::validcols(data = sample_data,threshold = 50)
```

## Example ```select_cols(dataset,threshold)```

This is a basic example which returns dataset after removing variables that contain missing values above the user defined threshold.

```{r}
nacleanr::select_cols(data = sample_data,threshold = 50)
```


## Example ```age_cal(dataset,variable)```

Calculates age by subtracting a year vector variable from current system year. Creates a new vector in dataset.

```{r}
building <- read_data(path = system.file("extdata", 'agedata.csv', package = "nacleanr"))
age <- age_cal(data = building, variable = "YearBuilt")
names(age)
building$age <- age$YearBuilt
head(building)

```

