---
title: "vignettes-for-nacleanR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignettes-for-nacleanR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## DESCRIPTION  
The goal of nacleanR is to provide functions that aide in data cleansing. It comprises of functions to   
* **Probe the percentage of missing values** within the variables  
* **Find valid & invalid variables** from point of view of percentage of missing data  
* **Remove Variables with Missing Values** above user defined limit from a dataset   
* **Calculate age variable in years** from an existing calendar year variable in dataset by subtracting year variable from System Date 


## Installation
*Update:Package is currently not available on CRAN*  
*Please use GitHub to install development version*  
You can install the released version of nacleanr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("nacleanR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("anandjage/nacleanR")
```
## Example ```perecnt_na(dataset)```

This is a basic example which shows how to find percentage of missing values in the form of NA in each variable:

```{r percent_na}
library(nacleanR)
csv <- system.file("extdata", 'nadata.csv', package = "nacleanR")
sample_data <- read_data(path = csv)
percent_na(sample_data)
```



## Example ```invalidcols(dataset,threshold)```
This is a basic example which shows variables that contain missing values NA above user defined threshold

```{r invalidcols}
library(nacleanR)
invalidcols(data = sample_data,threshold = 50)
```

## Example ```validcols(dataset,threshold)```
This is a basic example which shows variables that contain missing values NA in the form within the user defined threshold.

```{r validcols}
library(nacleanR)
validcols(data = sample_data,threshold = 50)
```

## Example ```select_cols(dataset,threshold)```

This is a basic example which returns dataset after removing variables that contain missing values above the user defined threshold.

```{r}
library(nacleanR)
new_data <- select_cols(data = sample_data,threshold = 50)
new_data
```


## Example ```age_cal(dataset,variable)```

Calculates age by subtracting a year vector variable from current system year. Creates a new vector in dataset.

```{r}
library(nacleanR)
csv = system.file("extdata", 'agedata.csv', package = "nacleanR")
agedata <- read_data(csv)
agedata$ageTodaySinceBuilt <- age_cal(agedata,"YearBuilt")
agedata$ageTodaySinceRenovated <- age_cal(agedata, "YearRenovated")
head(agedata)
```

